Forecasting the 2024 Election: Trump Dominates the South, Harris Leads in the Midwest

### 2024-10-20 paper/paper.qmd
committing changes to readme

---
title: "2024 US Presidential Election Model"
subtitle: "My subtitle if needed"
author: 
  - Jimin Lee
  - Sarah Ding
  - Xiyan Chen
thanks: "Code and data are available at: [https://github.com/jamiejiminlee/2024_US_Elections.git](https://github.com/jamiejiminlee/2024_US_Elections.git)."
date: today
date-format: long
abstract: "This paper presents a predictive model for the 2024 United States Presidential Election using state-level polling data. By aggregating high-quality polls, we predict the likely winner between Donald Trump and Kamala Harris in each state. A logistic regression model estimates the probability of Trump winning, with polling percentages as predictor variables. The model’s results highlight key battleground states and offer insights into voter dynamics, while also reflecting on the limitations of polling data in forecasting political outcomes."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

@fig-statemap shows the predicted winner of the 2024 US Presidential Election by state, based on a logistic regression model using aggregated polling data for Donald Trump and Kamala Harris. States where Trump is predicted to win are shown in red, while states where Harris is predicted to win are displayed in blue. States in gray represent missing or incomplete polling data, where predictions were not possible. According to the model, Trump is expected to win key states, including Florida, Missouri, and Montana, while Harris is forecasted to lead in Michigan, Virginia, and Pennsylvania.

>>>>

---
title: "Forecasting the 2024 Election: Trump Dominates the South, Harris Leads in the Midwest"
author: 
  - Jimin Lee
  - Sarah Ding
  - Xiyan Chen
thanks: "Code and data are available at: [https://github.com/jamiejiminlee/2024_US_Elections.git](https://github.com/jamiejiminlee/2024_US_Elections.git)."
date: today
date-format: long
abstract: "This paper presents a predictive model for the 2024 United States Presidential Election using state-level polling data. By aggregating high-quality polls, we predict the likely winner between Donald Trump and Kamala Harris in each state. A logistic regression model estimates the probability of Trump winning, with polling percentages as predictor variables. The model’s results highlight key battleground states and offer insights into voter dynamics, while also reflecting on the limitations of polling data in forecasting political outcomes."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

@fig-statemap shows the predicted winner of the 2024 US Presidential Election by state on a map [@usmap], based on a logistic regression model using aggregated polling data for Donald Trump and Kamala Harris. States where Trump is predicted to win are shown in red, while states where Harris is predicted to win are displayed in blue. States in gray represent missing or incomplete polling data, where predictions were not possible. According to the model, Trump is expected to win key states, including Florida, Missouri, and Montana, while Harris is forecasted to lead in Michigan, Virginia, and Pennsylvania.
